Why shouldn't you use numerical tests to diagnose the linear regression models?

### 2022-06-30 paper_comparison/paper_comparison/paper_comparison.Rmd
update paper

```{r}
library(tidyverse)
library(visage)
pilot <- read_csv(here::here("data/processed/processed_pilot.csv"))
survey <- read_csv(here::here("data/processed/processed_surveys.csv"))
sim_conv <- read_csv(here::here("data/processed/sim_conv_result.csv"), col_types = "dddddcdddlcdcdddlc")
```

```{r}
survey <- survey %>%
  mutate(log_effect_size = log(effect_size))

sim_conv <- sim_conv %>%
  mutate(log_effect_size = log(effect_size))

lineup_info <- select(survey, type:answer, conventional_p_value, ori_difficulty, exp, exp_lineup_id, log_effect_size) %>%
  group_by(exp_lineup_id) %>% 
  filter(row_number() == 1) %>%
  ungroup()

write_csv(lineup_info, here::here("data/processed/processed_lineup_info.csv"))

# Local constant estimator
kernel_regression_cubic <- function(sim_conv, h = 0.3, x = quote(log_effect_size)) {
  with(filter(sim_conv, type == "cubic", log_effect_size > -5, log_effect_size < 10),
     KernSmooth::locpoly(x = eval(x), y = reject, bandwidth = h, degree = 0, gridsize = 1000)) %>%
    as_tibble() %>%
    mutate(type = "cubic", h = h) %>%
    rename(reject = y)
}

# Local constant estimator
kernel_regression_heter <- function(sim_conv, h = 0.4, x = quote(log_effect_size)) {
  with(filter(sim_conv, type != "cubic", log_effect_size > -3),
     KernSmooth::locpoly(x = eval(x), y = reject, bandwidth = h, degree = 0, gridsize = 1000)) %>%
    as_tibble() %>%
    mutate(type = "heteroskedasticity", h = h) %>%
    rename(reject = y)
}
```

```{r}
if (file.exists(here::here("data/processed/lineup_env.rds"))) {
  env <- readRDS(here::here("data/processed/lineup_env.rds"))
} else {
  env <- new.env()
}

save_lineup_env <- function(env) {
  saveRDS(env, here::here("data/processed/lineup_env.rds"))
}

survey_pvalue <- survey %>%
  calc_p_value_multi(lineup_id = "exp_lineup_id", 
                     detected = "detect", 
                     n_sel = "num_selection",
                     comb = TRUE,
                     n_eval = 1:5,
                     n_sim = 100000,
                     cache_env = env) %>%
  rename(exp_lineup_id = lineup_id) %>%
  unnest_longer(col = p_value) %>%
  left_join(lineup_info) %>%
  mutate(reject = eval_p_value(p_value, tol = 0.01))

save_lineup_env(env)
```

```{r results='asis'}
map(1:5, function(x) glm(reject ~ log_effect_size,
                         family = binomial(),
                         data = filter(survey_pvalue, n_eval == {{x}}, type == "cubic"))) %>%
  stargazer::stargazer(header = FALSE,
            label = "tab:powerglmcubic",
            title = "Logistic regressions with rejection as response variable and natural logarithm of the effect size as regressor fitted on the data collected from experiment I and II for cubic model. Five regression were fitted for different number of evaluations.",
            style = "default",
            column.labels = c("num\\_eval: 1", "num\\_eval:2", "num\\_eval: 3", "num\\_eval: 4", "num\\_eval:5"),
            model.numbers = FALSE)
```

```{r results="asis"}
map(1:5, function(x) glm(reject ~ log_effect_size,
                         family = binomial(),
                         data = filter(survey_pvalue, n_eval == {{x}}, type == "heteroskedasticity"))) %>%
  stargazer::stargazer(header = FALSE,
            label = "tab:powerglmheter",
            title = "Logistic regressions with rejection as response variable and natural logarithm of the effect size as regressor fitted on the data collected from experiment I and II for heteroskedasticity model. Five regression were fitted for different number of evaluations.",
            style = "default",
            column.labels = c("num\\_eval: 1", "num\\_eval:2", "num\\_eval: 3", "num\\_eval: 4", "num\\_eval:5"),
            model.numbers = FALSE)
```

```{r power-com, fig.cap="\\label{fig:power-com}power com"}
survey_pvalue %>%
  mutate(reject = as.numeric(reject)) %>%
  mutate(n_eval = factor(n_eval)) %>%
  ggplot() +
  geom_point(aes(log_effect_size, reject), alpha = 0.01) +
  geom_line(data = kernel_regression_cubic(sim_conv, 0.4), aes(x, reject), linetype = 2) +
  geom_line(data = kernel_regression_heter(sim_conv, 0.75), aes(x, reject), linetype = 2) +
  geom_smooth(aes(log_effect_size, reject, group = n_eval, col = n_eval),
              method = "glm", method.args = list(family = binomial), size = 0.5, se = FALSE) +
  scale_colour_viridis_d(option = "B", begin = 0.5, end = 0.9) +
  facet_wrap(~type, scales = "free_x") +
  ylab("Estimated power")
```

```{r cubic-hard, fig.cap="\\label{fig:cubic-hard}cubic-hard ans 11"}
big_lineup_dat <- readRDS(here::here("data/big_study/all_data_big.RDS"))

# ans 11, conventional 0.003491033
CUBIC_MODEL$plot_lineup(mutate(big_lineup_dat[[28]]$data, .fitted = .pred),
                        remove_axis = TRUE,
                        theme = theme_light(),
                        remove_grid_line = TRUE)

@@

```{r heter-hard, fig.cap="\\label{fig:heter-hard}heter-hard ans 2"}
# ans 2, conventional 0.003535915
HETER_MODEL$plot_lineup(mutate(big_lineup_dat[[136]]$data, .fitted = .pred),
                        remove_axis = TRUE,
                        theme = theme_light(),
                        remove_grid_line = TRUE)
```

```{r power-com-cubic-a, fig.cap="\\label{fig:power-com-cubic-a}power com cubic a"}
bind_grid <- expand.grid(n = c(50, 100, 300),
                         h = 0.4,
                         x = c(quote(abs(a)/e_sigma)))

bind_list <- list()

for (i in 1:nrow(bind_grid)) {
  (function(n, h, x) {
    mutate(kernel_regression_cubic(filter(sim_conv, n == {{n}}), h = h, x = x),
           n = factor(n, levels = c(50, 100, 300)))
    })(n = bind_grid$n[i], h = bind_grid$h[i], x = bind_grid$x[[i]]) -> bind_list[[i]]
}

bind_sim <- reduce(bind_list, bind_rows)

# cubic break down
survey_pvalue %>%
  filter(type == "cubic") %>%
  mutate(n = factor(n, levels = c(50, 100, 300))) %>%
  mutate(n_eval = factor(n_eval)) %>%
  mutate(reject = as.numeric(reject)) %>%
  ggplot() +
  ggbeeswarm::geom_quasirandom(aes(abs(a)/e_sigma, reject, group = n), groupOnX = FALSE, alpha = 0.01) +
  geom_smooth(aes(abs(a)/e_sigma, reject, col = n_eval), method = "glm", method.args = list(family = binomial()), se = FALSE) +
  geom_line(data = bind_sim, aes(x, reject), col = "grey", linetype = 2, size = 1) +
  facet_wrap(~n, labeller = label_both) +
  scale_colour_viridis_d(option = "B", begin = 0.5, end = 0.9) +
  theme_light()
```

```{r power-com-cubic-b, fig.cap="\\label{fig:power-com-cubic-b}power com cubic b"}
bind_grid <- expand.grid(n = c(50, 100, 300),
                         h = 0.4,
                         x = c(quote(abs(b)/e_sigma)))

bind_list <- list()

for (i in 1:nrow(bind_grid)) {
  (function(n, h, x) {
    mutate(kernel_regression_cubic(filter(sim_conv, n == {{n}}), h = h, x = x),
           n = factor(n, levels = c(50, 100, 300)))
    })(n = bind_grid$n[i], h = bind_grid$h[i], x = bind_grid$x[[i]]) -> bind_list[[i]]
}

bind_sim <- reduce(bind_list, bind_rows)

# cubic break down
survey_pvalue %>%
  filter(type == "cubic") %>%
  mutate(n = factor(n, levels = c(50, 100, 300))) %>%
  mutate(reject = as.numeric(reject)) %>%
  mutate(n_eval = factor(n_eval)) %>%
  ggplot() +
  ggbeeswarm::geom_quasirandom(aes(abs(b)/e_sigma, reject, group = n), groupOnX = FALSE, alpha = 0.01) +
  geom_smooth(aes(abs(b)/e_sigma, reject, col = n_eval), method = "glm", method.args = list(family = binomial()), se = FALSE) +
  geom_line(data = bind_sim, aes(x, reject), col = "grey", linetype = 2, size = 1) +
  facet_wrap(~n, labeller = label_both) +
  scale_colour_viridis_d(option = "B", begin = 0.5, end = 0.9) +
  theme_light()
```

```{r eval = FALSE}
# cubic break down
# We do not have enough observations
survey_pvalue %>%
  filter(type == "cubic") %>%
  mutate(n = factor(n)) %>%
  mutate(reject = as.numeric(reject)) %>%
  ggplot() +
  geom_point(aes(abs(a), reject, col = n), alpha = 0.1) +
  geom_smooth(aes(abs(a), reject, col = n), method = "glm", method.args = list(family = binomial()), se = FALSE) +
  geom_smooth(data = mutate(filter(sim_conv, type == "cubic"), n = factor(n), reject = as.numeric(reject)),
              aes(abs(a), reject, group = n), 
              method = "glm", method.args = list(family = binomial()), se = FALSE, col = "grey", linetype = 2) +
  facet_grid(e_sigma~n)
```

```{r power-com-heter-b, fig.cap="\\label{fig:power-com-heter-b}power com heter b"}
bind_grid <- expand.grid(n = c(50, 100, 300),
                         h = 3,
                         x = c(quote(b)),
                         a = c(-1, 0, 1))

bind_list <- list()

for (i in 1:nrow(bind_grid)) {
  (function(n, h, x, a) {
    mutate(kernel_regression_heter(filter(sim_conv, n == {{n}}, a == {{a}}), h = h, x = x),
           n = factor(n, levels = c(50, 100, 300)),
           a = factor(a, levels = c(-1, 0, 1)))
    })(n = bind_grid$n[i], h = bind_grid$h[i], x = bind_grid$x[[i]], a = bind_grid$a[i]) -> bind_list[[i]]
}

bind_sim <- reduce(bind_list, bind_rows)

# heter break down
survey_pvalue %>%
  filter(type != "cubic") %>%
  mutate(n = factor(n, levels = c(50, 100, 300))) %>%
  mutate(reject = as.numeric(reject)) %>%
  mutate(n_eval = factor(n_eval)) %>%
  ggplot() +
  ggbeeswarm::geom_quasirandom(aes(b, reject, group = n), groupOnX = FALSE, alpha = 0.01) +
  geom_smooth(aes(b, reject, col = n_eval), method = "glm", method.args = list(family = binomial()), se = FALSE) +
  geom_line(data = bind_sim, aes(x, reject), col = "grey", linetype = 2, size = 1) +
  theme_light() +
  scale_colour_viridis_d(option = "B", begin = 0.5, end = 0.9) +
  facet_grid(a~n, labeller = label_both)
```

>>>>

```{r}
library(tidyverse)
library(visage)

set.seed(10086)
```

```{r get-conv-result}
stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1

if (!file.exists(here::here("data/third_study/conv_result.rds"))) {
  conv_result <- map(1:100000,
                   function(x) {
                     shape <- sample(1:4, 1)
                     e_sigma <- sample(c(0.5, 1, 2, 4), 1)
                     x_dist <- sample(c("uniform", "normal", "lognormal", "even_discrete"), 1)
                     x <- switch(x_dist,
                                 uniform = rand_uniform(-1, 1),
                                 normal = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))},
                                 lognormal = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))},
                                 even_discrete = rand_uniform_d(k = 5, even = TRUE))
                     mod <- poly_model(shape, x = x, sigma = e_sigma)
                     n <- sample(c(50, 100, 300), 1)
                     tmp_dat <- mod$gen(n)

                     tibble(shape = shape,
                            e_sigma = e_sigma,
                            x_dist = x_dist,
                            n = n,
                            effect_size = mod$effect_size(tmp_dat),
                            reject = mod$test(tmp_dat)$p_value < 0.05)
                   }) %>%
  reduce(bind_rows) %>%
  mutate(reject = as.numeric(reject))

  saveRDS(conv_result, here::here("data/third_study/conv_result.rds"))
} else {
  conv_result <- readRDS(here::here("data/third_study/conv_result.rds"))
}

@@

```{r get-third-result}
if (!file.exists(here::here("data/third_study/polynomials_lineup.rds"))) {
  polynomials_lineup <- get_polynomials_lineup()
  saveRDS(polynomials_lineup, here::here("data/third_study/polynomials_lineup.rds"))
} else {
  polynomials_lineup <- readRDS(here::here("data/third_study/polynomials_lineup.rds"))
}
```

```{r power-vs-log-effect-size}
polynomials %>%
  group_by(lineup_id) %>%
  summarise(across(c(type:p_value), first)) %>%
  filter(lineup_id < 577) %>%
  mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>%
  ggplot() +
  geom_smooth(aes(log(effect_size), reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_smooth(data = conv_result, aes(log(effect_size), reject, col = "Conventional test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  xlab("Natural logarithm of effect size") +
  ylab("Power")
```

```{r power-vs-log-effect-size-given-x-dist}
polynomials %>%
  group_by(lineup_id) %>%
  summarise(across(c(type:p_value), first)) %>%
  filter(lineup_id < 577) %>%
  mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>%
  ggplot() +
  geom_smooth(aes(log(effect_size), reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_smooth(data = conv_result, aes(log(effect_size), reject, col = "Conventional test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  facet_wrap(~x_dist) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  ggtitle("Power comparison conditional on the distribution of X")
```

```{r power-of-visual-test-given-x-dist}
polynomials %>%
  group_by(lineup_id) %>%
  summarise(across(c(type:p_value), first)) %>%
  filter(lineup_id < 577) %>%
  mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>%
  ggplot() +
  geom_smooth(aes(log(effect_size), reject, col = x_dist), method = "glm", method.args = list(family = binomial), se = FALSE) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  ggtitle("Power of visual test conditional on the distribution of X")
```

```{r power-vs-log-effect-size-given-shape}
polynomials %>%
  group_by(lineup_id) %>%
  summarise(across(c(type:p_value), first)) %>%
  filter(lineup_id < 577) %>%
  mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>%
  ggplot() +
  geom_smooth(aes(log(effect_size), reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_smooth(data = conv_result, aes(log(effect_size), reject, col = "Conventional test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  facet_wrap(~shape) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  ggtitle("Power comparison conditional on the shape of the Hermite polynomials")
```

```{r power-of-visual-test-given-shape}
polynomials %>%
  group_by(lineup_id) %>%
  summarise(across(c(type:p_value), first)) %>%
  filter(lineup_id < 577) %>%
  mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01)), shape = factor(shape)) %>%
  ggplot() +
  geom_smooth(aes(log(effect_size), reject, col = shape), method = "glm", method.args = list(family = binomial), se = FALSE) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  ggtitle("Power of visual test conditional on the shape of the Hermite polynomials")
```

```{r power-vs-log-effect-size-given-number-of-observations}
polynomials %>%
  group_by(lineup_id) %>%
  summarise(across(c(type:p_value), first)) %>%
  filter(lineup_id < 577) %>%
  mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01))) %>%
  ggplot() +
  geom_smooth(aes(log(effect_size), reject, col = "Visual test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  geom_smooth(data = conv_result, aes(log(effect_size), reject, col = "Conventional test"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  facet_wrap(~n) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  ggtitle("Power comparison conditional on the number of observations")
```

```{r power-of-visual-test-given-number-of-observations}
polynomials %>%
  group_by(lineup_id) %>%
  summarise(across(c(type:p_value), first)) %>%
  filter(lineup_id < 577) %>%
  mutate(reject = as.numeric(eval_p_value(p_value, tol = 0.01)), n = factor(n)) %>%
  ggplot() +
  geom_smooth(aes(log(effect_size), reject, col = n), method = "glm", method.args = list(family = binomial), se = FALSE) +
  xlab("Natural logarithm of effect size") +
  ylab("Power") +
  ggtitle("Power of visual test conditional on the number of observations")
```

### 2022-06-30 paper_comparison/paper_comparison/paper_comparison.tex
update paper

The previous section focuses on the change of effect size relative to
the power of the visual test.

\begin{table}[!htbp] \centering 
  \caption{Logistic regressions with rejection as response variable and natural logarithm of the effect size as regressor fitted on the data collected from experiment I and II for cubic model. Five regression were fitted for different number of evaluations.} 
  \label{tab:powerglmcubic} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{5}{c}{\textit{Dependent variable:}} \\ 
\cline{2-6} 
\\[-1.8ex] & \multicolumn{5}{c}{reject} \\ 
 & num\_eval: 1 & num\_eval:2 & num\_eval: 3 & num\_eval: 4 & num\_eval:5 \\ 
\hline \\[-1.8ex] 
 log\_effect\_size & 0.929$^{***}$ & 1.258$^{***}$ & 1.096$^{***}$ & 1.113$^{***}$ & 1.244$^{***}$ \\ 
  & (0.073) & (0.076) & (0.054) & (0.056) & (0.077) \\ 
  & & & & & \\ 
 Constant & $-$1.969$^{***}$ & $-$2.534$^{***}$ & $-$1.549$^{***}$ & $-$1.334$^{***}$ & $-$1.404$^{***}$ \\ 
  & (0.169) & (0.173) & (0.113) & (0.122) & (0.185) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 630 & 1,135 & 1,660 & 1,904 & 1,879 \\ 
Log Likelihood & $-$220.882 & $-$314.394 & $-$471.152 & $-$396.979 & $-$206.296 \\ 
Akaike Inf. Crit. & 445.764 & 632.788 & 946.305 & 797.958 & 416.592 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{table}[!htbp] \centering 
  \caption{Logistic regressions with rejection as response variable and natural logarithm of the effect size as regressor fitted on the data collected from experiment I and II for heteroskedasticity model. Five regression were fitted for different number of evaluations.} 
  \label{tab:powerglmheter} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{5}{c}{\textit{Dependent variable:}} \\ 
\cline{2-6} 
\\[-1.8ex] & \multicolumn{5}{c}{reject} \\ 
 & num\_eval: 1 & num\_eval:2 & num\_eval: 3 & num\_eval: 4 & num\_eval:5 \\ 
\hline \\[-1.8ex] 
 log\_effect\_size & 0.821$^{***}$ & 1.104$^{***}$ & 1.157$^{***}$ & 1.387$^{***}$ & 1.651$^{***}$ \\ 
  & (0.086) & (0.079) & (0.066) & (0.076) & (0.110) \\ 
  & & & & & \\ 
 Constant & $-$4.472$^{***}$ & $-$5.887$^{***}$ & $-$5.431$^{***}$ & $-$6.154$^{***}$ & $-$7.123$^{***}$ \\ 
  & (0.434) & (0.415) & (0.344) & (0.400) & (0.591) \\ 
  & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 630 & 1,138 & 1,596 & 1,662 & 1,416 \\ 
Log Likelihood & $-$333.119 & $-$631.519 & $-$835.317 & $-$650.570 & $-$342.058 \\ 
Akaike Inf. Crit. & 670.238 & 1,267.038 & 1,674.634 & 1,305.140 & 688.116 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/power-com-1.pdf}
\caption{\label{fig:power-com}power com}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/cubic-hard-1.pdf}
\caption{\label{fig:cubic-hard}cubic-hard ans 11}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/heter-hard-1.pdf}
\caption{\label{fig:heter-hard}heter-hard ans 2}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/power-com-cubic-a-1.pdf}
\caption{\label{fig:power-com-cubic-a}power com cubic a}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/power-com-cubic-b-1.pdf}
\caption{\label{fig:power-com-cubic-b}power com cubic b}
\end{figure}

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/power-com-heter-b-1.pdf}
\caption{\label{fig:power-com-heter-b}power com heter b}
\end{figure}

>>>>

The previous section focuses on the change of effect size relative to
the power of the visual test. However, effect size is only a one
dimensional summarisation of parameters used in data simulation.
Individual factor embedded in the simulation process should also be
analysed.

In cubic model, two major factors that influencing the strength of the
signal are \(a\) and \(b\). Figure \ref{fig:power-com-cubic-a} and
\ref{fig:power-com-cubic-a} illustrates 30 different logistic
regressions fit for different number of evaluations and different number
of observations \(n\). The regressor used in these models was
\(|a|/\sigma\) since the noise level \(\sigma\) needed to be taken into
account. From the figures, we can observe \ldots{}

\includegraphics{paper_comparison_files/figure-latex/power-vs-log-effect-size-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/power-vs-log-effect-size-given-x-dist-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/power-of-visual-test-given-x-dist-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/power-vs-log-effect-size-given-shape-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/power-of-visual-test-given-shape-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/power-vs-log-effect-size-given-number-of-observations-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/power-of-visual-test-given-number-of-observations-1.pdf}
